Integrating spatial and temporal information to make ecological forecasts

### 2018-02-27 doc/manuscript.tex
Small additions to manuscript

Genotype frequencies will shift across a gradient of mean annual temperature: cold sites will be dominated by the cold-loving genotype, warm sites will be dominated by the heat-loving genotype, and intermediate sites will be dominated by the heterozygous genotype (Fig. \ref{fig:SpatialPattern}).

@@

>>>>

Genotype frequencies will shift across a gradient of mean annual temperature: cold sites will be dominated by the cold-loving homozygous genotype, warm sites will be dominated by the heat-loving homozygous genotype, and intermediate sites will be dominated by the heterozygous genotype (Fig. \ref{fig:SpatialPattern}).

@@

This spatial pattern is the outcome of steady-state conditions. At any one site, the population's short-term response to temperature will be determined by the dominant genotype's reaction norm. For example, at a cold site dominated by the cold-loving homozygous genotype, a warmer than normal year would cause a decrease in population size, even though the heat-loving homozygote might perform optimally at that temperature. If warmer than normal conditions persist for many years, then genotype frequencies will shift, and the heat-loving homozygote will compensate for the decreases of the cold-loving genotype.
